Spin canonical rings of log stacky curves

### 2015-07-14 curves-write-up/spin-cring.tex
edit to idea of proof in monster lemma

\sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$. Then, $\subseteq$ follows from condition $(3)$ and the fact that no terms in $S$ can be contained in $\initial(I)$ because $(1)$ implies that $S$ is a basis.

@@

Next, part (b) immediately follows from the conclusion of Lemma ~\ref{lem:relations_from_generators_induction}, reducing the proof to verifying the hypotheses of that lemma. 
The first two hypotheses follow immediately from the definition of block order. Checking the third condition is quite technical, but the conditions follow from certain slope conditions, given by ~\ref{custom:sat-1-*}, ~\ref{custom:sat-1-**}, and ~\ref{custom:sat-1-***}.

@@

\sssec*{Idea of Proof:}
We check the theorem in two cases, depending on whether $\Delta > 0$.
If $\Delta > 0$, we first check that the theorem holds for $\halfcan_X$
by inductively adding in log points to the base case of $\halfcan_X'
= 0$. Then we check that it holds for $\halfcan$ by raising
the stabilizer orders of stacky points in a sequence of steps. When
raising the stacky orders, it is important that we increment the
stabilizer orders of the maximum possible number of stacky points
at each step, so that the corresponding set will remain admissible.
The check for $\Delta = 0$ is similar, although in this case we do
not need to add in log points, only stacky points, and we will need
to utilize the base cases from Subsection ~\ref{ssec:g-1_base}.

>>>>

\sssec*{Idea of Proof:} To show $\supseteq$, we show that $T \subseteq \initial(I)$, which follows immediately from $(1)$ and $(2)$.
We deduce $\subseteq$ by noting that we can reduce any monomial in $k[x_1, \ldots, x_m, y_1, \ldots, y_n]$ to a monomial in the basis $S$ via a set of relations whose initial terms include each monomial in $\initial(I')\Bk[x_1, \ldots, x_m, y_1, \ldots, y_n] + \langle T \rangle$.

@@

Next, part (b) immediately follows from the conclusion of Lemma
~\ref{lem:relations_from_generators_induction}, reducing the proof
to verifying the hypotheses of that lemma. The first two hypotheses
follow immediately from the definition of block order. Checking the
third condition is quite technical, but follows from the construction of $V$ and the $U_i$'s.

@@

\sssec*{Idea of Proof:}
We check the theorem in two cases, depending on whether $\Delta > 0$.
If $\Delta > 0$, we first check that the theorem holds for $\halfcan_X$
by inductively adding in log points to the base case of $\halfcan_X'
= 0$. Then we check that the theorem holds for $\halfcan$ by adding
stacky points and then inductively raising the stabilizer orders of
stacky points in the following sequence of steps. When
raising the stacky orders, it is important that we increment the
stabilizer orders of the maximum possible number of stacky points
at each step, so that the corresponding set will remain admissible.
The check for $\Delta = 0$ is similar, although in this case we do
not need to add in log points, only stacky points, and we will need
to utilize the base cases from Subsection ~\ref{ssec:g-1_base}.
